\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 related.tex
heading changes based on Minh and discussion; also noted FP comments

There are costs associated with such inference based control are also
not inconsequential. Foremost among them is the steep learning curve
that comes with the design of the domain model. With limited support
tools necessary for knowledge capture and design of the constraints
often in stylized higher-level languages (see \cite{NDDL} for an
example), it requires the modeler to think in alternative ways to do
problem solving. More importantly it is often necessary for the
modeler to be exposed to the internal representation of the planner
and how it performs search. THe level of expertise is often well above
what would be expected of a typical well-rounded Computer Science
graduate student.

@@

Planning and plan execution are not new to the overall field of
robotics. Early motivation of building computational mechanisms for
decision making were intended to be deployed on robotic devices by
very definition. The seminal volume \cite{computersthought} very
clearly articulates how physical manifestation of robots could be
controlled for task planning and execution. The very first planner
\cite{green69} was an exercise in computational theorem proving with
early state space planners popularized by \texttt{STRIPS}
\cite{strips71} dominating the academic landscape. An early
demonstration of planning as a situated agent was the highly
influential \texttt{Shakey} the robot experiment
\cite{shakey84}. Subsequent work driven largely by defense funding in
the United States sequestered the discipline in academic labs
principally applied for algorithmic development and if embedded then
in testing within the confines of modest indoor settings. The leap to
applying them for real world problem solving is relatively new and
driven largely by NASA applications pioneered by \cite{mus94,mus98,
  jonsson00, rajan00, chien05, bresina05}.

The dominant approach for building agent control systems utilize a
$3$-layered architecture (see \cite{gat98} for a well thought out
rationale), notable examples of which include \texttt{IPEM}
\cite{AmbrosIngerson88}, \texttt{ROGUE} \cite{Haigh98}, the LAAS
Architecture \cite{alami:1998p820}, the Remote Agent Experiment
\texttt{RAX} \cite{mus98} and the Autonomous Spacecraft Experiment
\texttt{ASE} \cite{chien99} (see \cite{Knight01} for a survey). Early
efforts were cognizant of if absent with, dealing with time and
resources for such experiments.

@@

Our system, \texttt{T-REX}, the focus of this chapter, is an agent
control structure formally defined as a composition of coordinated
control loops with a recurring sense-plan-act (SPA) cycle with
deliberation at its core. \texttt{T-REX} was designed after carefully
evaluating lessons learned from \texttt{IDEA} and owes substantially
to the notion of partitioned problem solving from that effort. However
this partitioning is systematic and methodologically principled where
we manage the information flow within the partitioned structure to
ensure consistency in order to direct the flow of goals and
observations in a timely manner. The resulting control structure
improves scalability since many details of each controller can be
encapsulated within a single control loop.  Furthermore, partitioning
increases robustness since controller failure can be localized to
enable graceful system degradation, making this an effective
\emph{divide-and-conquer} approach to the overall control problem.

A recent variation of the key idea of such controller composition
derived from \texttt{T-REX} is \texttt{ROAR} \cite{degroote11} where
lower-level functional modules that control specific sensors are
organized within a graph hierarchy. One reason they cite such a
structure is essential is in dealing robustly to failure; an
off-nominal condition will allow rapid graph traversal to identify
alternative ways in which sensing tasks can be executed and therefore
aiding in responsiveness. However, it is unclear whether to date this
system actually deliberates and whether it is actually instantiated on
a real platform for control.

>>>>

There are costs associated with such inference based control which are
not inconsequential. Foremost among them is the steep learning curve
that comes with the design of the domain model. With limited support
tools necessary for knowledge capture and design of the constraints
often in stylized higher-level languages (see \cite{NDDL} for an
example), it requires the modeler to think in alternative ways to do
problem solving. More importantly it is often necessary for the
modeler to be exposed to the internal representation of the planner
and how it performs search. The level of expertise is often well above
what would be expected of a typical well-rounded Computer Science
graduate student. Yet in our experience, the cost of model design in
such systems, is well balanced against the cost of re-engineering new
mission scripts for new deployment in more ``classical'' script-based
controllers.

@@

Planning and plan execution are not new to the overall field of
robotics. Early motivation of building computational mechanisms for
decision making were intended to be deployed on robotic devices by
very definition. The seminal volume \cite{computersthought} very
clearly articulates how physical manifestation of robots could be
controlled by task planning and execution. The very first planner
\cite{green69} was an exercise in computational theorem proving with
early state space planners popularized by \texttt{STRIPS}
\cite{strips71} dominating the academic landscape. An early
demonstration of planning as a situated agent was the highly
influential \texttt{Shakey} the robot experiment
\cite{shakey84}. Subsequent work driven largely by defense funding in
the United States sequestered the discipline in academic labs
principally applied for algorithmic development and if embedded then
in testing within the confines of modest indoor settings. The leap to
applying them for real world problem solving is relatively new and
driven largely by NASA applications pioneered by \cite{mus94,mus98,
  jonsson00, rajan00, chien05, bresina05}.

The dominant approach for building agent control systems utilize a
$3$-layered architecture (see \cite{gat98} for a well thought out
rationale), notable examples of which include \texttt{IPEM}
\cite{AmbrosIngerson88}, \texttt{ROGUE} \cite{Haigh98}, the LAAS
Architecture \cite{alami:1998p820}, the Remote Agent Experiment
\texttt{RAX} \cite{mus98} and the Autonomous Spacecraft Experiment
\texttt{ASE} \cite{chien99} (see \cite{Knight01} for a survey). % Early
% efforts were cognizant of if absent with, dealing with time and
% resources for such experiments.

@@

Our system, \rx, the focus of this chapter, is an agent control
structure formally defined as a composition of coordinated control
loops where sensing, planning and acting are resulting from concurrent
deliberating tasks within a formal framework.  \rx was designed after
carefully evaluating lessons learned from \texttt{IDEA} to which it
owes substantially the notion of partitioned problem solving. However
partitioning in \rx is systematic and methodologically principled
where we manage the information flow within the partitioned structure
to ensure consistency in order to direct the flow of goals and
observations in a timely manner. The resulting control structure
improves scalability since many details of each controller can be
encapsulated within a single control loop.  Furthermore, partitioning
increases robustness since controller failure can be localized to
enable graceful system degradation, making this an effective
\emph{divide-and-conquer} approach to the overall control problem.

A recent variation of the key idea of such controller composition
derived from \rx is \texttt{ROAR} \cite{degroote11} where lower-level
functional modules that control specific sensors are organized within
a graph hierarchy. One reason they cite such a structure is essential
is in dealing robustly to failure; an off-nominal condition will allow
rapid graph traversal to identify alternative ways in which sensing
tasks can be executed and therefore aiding in responsiveness. However,
it is unclear whether to date this system actually deliberates and
whether it is actually instantiated on a real platform for control.
